### 2016-12-07 paper/chapters/gan.tex
added GAN architecture image

% http://www.slideshare.net/xavigiro/deep-learning-for-computer-vision-generative-models-and-adversarial-training-upc-2016
% TODO: recreate in tikz
\begin{figure}[htb]
\centering
  \includegraphics[width=\linewidth]{media/deep-learning-for-computer-vision-generative-models-and-adversarial-training-upc-2016-5-638.jpg}
  \caption{Conceptual idea of generative adversarial networks (source: Summer seminar UPC TelecomBCN)}\label{fig:gan_architecture}
\end{figure}

>>>>

% http://www.slideshare.net/xavigiro/deep-learning-for-computer-vision-generative-models-and-adversarial-training-upc-2016
% TODO: recreate in tikz

\begin{figure}[htb]
\centering
\includestandalone[width=\linewidth,mode=buildnew]{media/gan_conceptual}
  \caption{Conceptual figure of generative adversarial network}
  \label{fig:gan_a}
  \medskip
  \small
  Figure is illustrating the information and gradient flow in the GAN framework.\\
  \emph{data space} denotes the real-world data, which we aim to model.
  Dashed arrows denote the gradient flow.
\end{figure}

%\begin{figure}[htb]
%\centering
%\includestandalone[mode=buildnew,width=\linewidth]{media/gan_conceptual}
  %\caption{Conceptual idea of generative adversarial networks (source: Summer seminar UPC TelecomBCN)}\label{fig:gan_architecture}
%\end{figure}
